### 2025-04-08 correlation.qmd
20250408 - noquote

pearson_r <- pearson_test$estimate
pearson_df <- pearson_test$parameter
pearson_p <- pearson_test$p.value
```

The $r$ value (`{r} petersenlab::apa(pearson_r, decimals = 2)`) is slightly negative.
The [effect size](#sec-practicalSignificance) of the association is small—for what is considered a small, medium, and large effect size for $r$ values, see @sec-effectSizeThresholds.
The $p$-value is less than .05, so it is a statistically significant correlation.
We could report this finding as follows: There was a statistically significant, weak negative association between height and fantasy points ($r[`{r} pearson_df`] = `{r} petersenlab::apa(pearson_r, decimals = 2)`$, $p < .001$); the taller a player was, the fewer fantasy points they tended to score.

>>>>

pearson_r <- pearson_test$estimate
pearson_df <- pearson_test$parameter
pearson_p <- pearson_test$p.value

#pValue <- function(value, digits = 3){
#    if(value < .001){
#      newValue <- " < .001"
#    } else {
#      newValue <- paste(
#        " = ",
#        petersenlab::suppressLeadingZero(specify_decimal(value, digits)),
#        sep = "")
#    }
#  
#    return(newValue)
#  }
#
#textCorrelation <- function(x, y, decimals = 2){
#  substitute(
#  paste(
#    italic(r), "(", valueDF, ")",  " = ", valueR,
#    ", ", italic(p), valueP,
#    sep = ""),
#  list(
#    valueR = noquote(sub("0.", ".", sprintf("%.2f", round(cor.test(x, y)$estimate[[1]], decimals)))),
#    valueDF = cor.test(x, y)$parameter[[1]],
#    valueP = pValue(cor.test(x, y)$p.value[[1]])
#    )
#  )
#}
#
#textCorrelation <- function(x, y, decimals = 2){
#  substitute(
#  paste(
#    r, "(", valueDF, ")",  " = ", valueR,
#    ", ", p, valueP,
#    sep = ""),
#  list(
#    valueR = noquote(sub("0.", ".", sprintf("%.2f", round(cor.test(x, y)$estimate[[1]], decimals)))),
#    valueDF = cor.test(x, y)$parameter[[1]],
#    valueP = pValue(cor.test(x, y)$p.value[[1]])
#    )
#  )
#}
#
#textCorrelation(player_stats_seasonal$height, player_stats_seasonal$fantasyPoints)
```

The $r$ value (`{r} petersenlab::apa(pearson_r, decimals = 2, leading = FALSE)`) is slightly negative.
The [effect size](#sec-practicalSignificance) of the association is small—for what is considered a small, medium, and large effect size for $r$ values, see @sec-effectSizeThresholds.
The $p$-value is less than .05, so it is a statistically significant correlation.
We could report this finding as follows: There was a statistically significant, weak negative association between height and fantasy points ($r(`{r} pearson_df`) = `{r} noquote(petersenlab::apa(pearson_r, decimals = 2, leading = FALSE))`$, $p < .001$); the taller a player was, the fewer fantasy points they tended to score.
